Usenet Project - CSV Cleaning

### 2024-08-25 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
cleaned up cleaning code

# Old Read and Merge (DONT RUN)
netmed_threads <- read.csv("CSV Files/Threads/netmed_threads.csv")
netmotss_threads <- read.csv("CSV Files/Threads/netmotss_threads.csv")
netnews_threads <- read.csv("CSV Files/Threads/netnews_threads.csv")
netpolitics_threads <- read.csv("CSV Files/Threads/netpolitics_threads.csv")
netreligion_threads <- read.csv("CSV Files/Threads/netreligion_threads.csv")
netsingles_threads <- read.csv("CSV Files/Threads/netsingles_threads.csv")

netmed_comments <- read.csv("CSV Files/Comments/netmed_comments.csv")
netmotss_comments <- read.csv("CSV Files/Comments/netmotss_comments.csv")
netnews_comments <- read.csv("CSV Files/Comments/netnews_comments.csv")
netpolitics_comments <- read.csv("CSV Files/Comments/netpolitics_comments.csv")
netreligion_comments <- read.csv("CSV Files/Comments/netreligion_comments.csv")
netsingles_comments <- read.csv("CSV Files/Comments/netsingles_comments.csv")

@@

write.csv(all_threads, file.path(threads_directory, "combined_threads.csv"), row.names = FALSE)
write.csv(all_comments, file.path(comments_directory, "combined_comments.csv"), row.names = FALSE)
---

---

# Maintainence

## Reset
```{r}
rm(list = ls()) 
setwd("/Users/emerson/Github/usenet_AIDs_discourses_webpage")
```

## Maintenance
```{r Load LIbraries, Directories, and Datasets}
# Load Libraries
library(tidyverse)
library(readr)
library(webshot)
library(htmltools)
library(ggplot2)
library(dplyr)
library(syuzhet)
library(sjPlot)

@@

# Additional Filtering
```{r Filter by Keyword}
# List of extended keywords and phrases
keywords <- c("aids", "hiv", "acquired immune deficiency syndrome", "human immunodeficiency virus",
              "gay plague", "gay cancer", "kaposi's sarcoma", "pneumocystis pneumonia",
              "homosexual disease", "gay disease", "gay fear", "fear of gay", "fear of homosexual",
              "sexual orientation disease")

# Function to flag comments with keywords
flag_keywords <- function(text) {
  # Convert text to lowercase
  text <- tolower(text)
  # Check if any keyword is present
  grepl(paste(keywords, collapse = "|"), text)
}

# Add a column to indicate if the comment contains any keyword
all_comments <- all_comments %>%
  mutate(Contains_Keyword = flag_keywords(Full.Text))

# Identify threads with at least one comment containing a keyword
threads_with_keywords <- all_comments %>%
  filter(Contains_Keyword) %>%
  distinct(Thread.ID) %>%
  pull(Thread.ID)

# Filter comments in threads with at least one keyword
comments_in_keyword_threads <- all_comments %>%
  filter(Thread.ID %in% threads_with_keywords)

# Group by newsgroup and calculate required statistics
keywords_summary_df <- comments_in_keyword_threads %>%
  group_by(newsgroup) %>%
  summarize(
    Comments_with_Keywords = sum(Contains_Keyword),
    Conversations_Mentioned_In = n_distinct(Thread.ID),
    Total_Comments_In_Threads = n(),
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100
  )

# Add a totals row
totals <- keywords_summary_df %>%
  summarize(
    newsgroup = "Total",
    Comments_with_Keywords = sum(Comments_with_Keywords),
    Conversations_Mentioned_In = sum(Conversations_Mentioned_In),
    Total_Comments_In_Threads = sum(Total_Comments_In_Threads),
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100
  )

# Print the keyword summary data frame with totals
print(keywords_summary_df)
```

```{r Save Keyword CSVs to File}
# Collect all related threads and comments
related_threads <- all_threads %>%
  filter(Unique_ThreadID %in% threads_with_keywords) %>%
  filter(Date <= as.Date("1988-12-31"))

related_comments <- all_comments %>%
  filter(Thread.ID %in% threads_with_keywords) %>%
  filter(Date <= as.Date("1988-12-31"))

# Write the related threads and comments to CSV files
write.csv(related_threads, file.path(threads_directory, "aids_related_threads.csv"), row.names = FALSE)
write.csv(related_comments, file.path(comments_directory, "aids_related_comments.csv"), row.names = FALSE)
```

@@

# Print the summary data frame with totals
tab_df(summary_df, file = paste0(output_directory, "Images and Tables/descriptive_statistics_table.html"))
```

>>>>

```{r Old Read and Merge, eval=FALSE, include=FALSE}
netmed_threads <- read.csv(file.path(threads_directory, "netmed_threads.csv")
netmotss_threads <- read.csv(file.path(threads_directory, "netmotss_threads.csv")
netnews_threads <- read.csv(file.path(threads_directory, "netnews_threads.csv")
netpolitics_threads <- read.csv(file.path(threads_directory, "netpolitics_threads.csv")
netreligion_threads <- read.csv(file.path(threads_directory, "netreligion_threads.csv")
netsingles_threads <- read.csv(file.path(threads_directory, "netsingles_threads.csv")

netmed_comments <- read.csv(file.path(comments_directory, "netmed_comments.csv")
netmotss_comments <- read.csv(file.path(comments_directory, "netmotss_comments.csv")
netnews_comments <- read.csv(file.path(comments_directory, "netnews_comments.csv")
netpolitics_comments <- read.csv(file.path(comments_directory, "netpolitics_comments.csv")
netreligion_comments <- read.csv(file.path(comments_directory, "netreligion_comments.csv")
netsingles_comments <- read.csv(file.path(comments_directory, "netsingles_comments.csv")

@@

write.csv(all_threads, file.path(threads_directory, "combined_threads.csv"), row.names = FALSE)
write.csv(all_comments, file.path(comments_directory, "combined_comments.csv"), row.names = FALSE)
```

# Maintainence
```{r Reset and Set Working Directory}
rm(list = ls()) 
knitr::opts_knit$set(root.dir = '/Users/emerson/Github/usenet_AIDs_discourses_webpage')
```

```{r Load LIbraries, Directories, and Datasets}
# Load Libraries
library(tidyverse)
library(readr)
library(webshot)
library(htmltools)
library(ggplot2)
library(dplyr)
library(syuzhet)
library(sjPlot)

@@

@@

# Print the summary data frame with totals
tab_df(summary_df, file = paste0(output_directory, "images and tables/descriptive_statistics_table.html"))
```

# Additional Filtering
```{r Filter by Keyword and Add Relevancy Scores}
# List of refined keywords and phrases (broad keywords removed)
keywords <- c("aids", "htlv", "hiv", "acquired immune deficiency syndrome", "human immunodeficiency virus",
              "gay plague", "gay cancer", "kaposi's sarcoma", "pneumocystis pneumonia",
              "homosexual disease", "gay disease", "gay fear", "fear of gay", "fear of homosexual",
              "sexual orientation disease", "virus", "sex", "promiscuity", "patients")

# Function to calculate relevancy score
calculate_relevancy <- function(text) {
  # Convert text to lowercase
  text <- tolower(text)
  # Check for the presence of each keyword
  keyword_matches <- sapply(keywords, function(keyword) grepl(keyword, text))
  # Calculate relevancy score as the number of keywords present
  relevancy_score <- sum(keyword_matches)
  return(relevancy_score)
}

# Step 1: Identify threads with at least one comment containing a keyword
all_comments_aids <- all_comments %>%
  rowwise() %>%
  mutate(Contains_Keyword = any(sapply(keywords, function(keyword) grepl(keyword, tolower(Full.Text)))))

# Filter threads containing at least one keyword
all_threads_aids <- all_comments_aids %>%
  filter(Contains_Keyword) %>%
  distinct(Thread.ID)

# Step 2: Fetch all comments from threads with at least one keyword-containing comment
comments_in_keyword_threads <- all_comments %>%
  filter(Thread.ID %in% all_threads_aids$Thread.ID)

# Step 3: Calculate relevancy score for each comment and add it to the dataframe
comments_in_keyword_threads <- comments_in_keyword_threads %>%
  rowwise() %>%
  mutate(Relevancy = calculate_relevancy(Full.Text))

# Save the comments dataframe to CSV
write.csv(comments_in_keyword_threads, file.path(comments_directory, "aids_related_comments.csv"), row.names = FALSE)

# Step 4: Calculate the average relevancy score for each thread
thread_relevancy_scores <- comments_in_keyword_threads %>%
  group_by(Thread.ID) %>%
  summarize(Thread_Relevancy = mean(Relevancy, na.rm = TRUE))

# Merge thread relevancy scores back to thread-level dataframe
threads_summary_df <- comments_in_keyword_threads %>%
  distinct(Thread.ID, newsgroup) %>%
  left_join(thread_relevancy_scores, by = "Thread.ID")

# Save the threads dataframe to CSV
write.csv(threads_summary_df, file.path(threads_directory, "aids_related_threads.csv"), row.names = FALSE)
```

```{r Keyword Descriptive Statistics}
# Step 5: Group by newsgroup and calculate required statistics, including thread relevancy
keywords_summary_df <- comments_in_keyword_threads %>%
  group_by(newsgroup) %>%
  summarize(
    Comments_with_Keywords = sum(Relevancy > 0),
    Conversations_Mentioned_In = n_distinct(Thread.ID),
    Total_Comments_In_Threads = n(),
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
    Average_Relevancy_Score = mean(Relevancy, na.rm = TRUE)
  )

# Merge thread relevancy averages back to the summary dataframe
threads_summary_df_grouped <- threads_summary_df %>%
  group_by(newsgroup) %>%
  summarize(Average_Thread_Relevancy = mean(Thread_Relevancy, na.rm = TRUE))

# Combine comment and thread summaries
keywords_summary_df <- keywords_summary_df %>%
  left_join(threads_summary_df_grouped, by = "newsgroup")

# Add a totals row
totals <- keywords_summary_df %>%
  summarize(
    newsgroup = "Total",
    Comments_with_Keywords = sum(Comments_with_Keywords),
    Conversations_Mentioned_In = sum(Conversations_Mentioned_In),
    Total_Comments_In_Threads = sum(Total_Comments_In_Threads),
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
    Average_Relevancy_Score = mean(Average_Relevancy_Score, na.rm = TRUE),
    Average_Thread_Relevancy = mean(Average_Thread_Relevancy, na.rm = TRUE)
  )

# Print the keyword summary data frame with totals
tab_df(keywords_summary_df, file = paste0(output_directory, "images and tables/aids_descriptive_statistics_table.html"))
```
